Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-22 latex/article.tex
template

\documentclass{llncs}
\usepackage{enumerate}% http://ctan.org/pkg/enumerate
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage{url}
\usepackage{overpic}
\usepackage{enumerate}
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{tikz}        % standard LaTeX graphics tool
%\usetikzlibrary{arrows}
%\usetikzlibrary{quotes,angles}
\usepackage{subfigure}                                 % authors: subfigures
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}   % authors: last version of algorithm display
\usepackage{todonotes}

@@

@@

>>>>

\documentclass{llncs}
\usepackage{enumerate}% http://ctan.org/pkg/enumerate
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage{url}
\usepackage{overpic}
\usepackage{enumerate}
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{tikz}        % standard LaTeX graphics tool
\usepackage{pgfplots}

%\usetikzlibrary{arrows}
%\usetikzlibrary{quotes,angles}
\usepackage{subfigure}                                 % authors: subfigures
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}   % authors: last version of algorithm display
\usepackage{todonotes}

\usepackage{booktabs}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{@{}lrrrrrr@{}}
      \toprule
    Quantities & H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches & & & & & &\\
      Time (in ms) & & & & & &\\
      $L_\infty$ error (\wrt $l_0$) & & & & & &\\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{object, size, radius, full res, num of vertices (timings
    only consider the curvature estimation step).\label{tab:full-res-stat}}
\end{table}

@@

\begin{figure}[!htbp]
  \begin{center}
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
	  bar width=15pt,
	  nodes near coords,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.20)},
            anchor=north,legend columns=-1},
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R1, Octa-R2, Snow-R1, Snow-R2, 
	    xxx-R1, xxx-R2},
          xtick=data,
          x tick label style={rotate=45,anchor=east},
        ]
        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,2) 
          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,0)};
        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,0) 
          (Snow-R1,0) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,0)};
        \addplot+[ybar] plot coordinates {(Octa-R1,6) (Octa-R2,6)
          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
        \addplot+[ybar] plot coordinates {(Octa-R1,4) (Octa-R2,2) 
          (Snow-R1,0) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
    \end{tikzpicture}
     \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
	  bar width=15pt,
	  nodes near coords,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.20)},
            anchor=north,legend columns=-1},
         % ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R1, Octa-R2, Snow-R1, Snow-R2, 
	    xxx-R1, xxx-R2},
          xtick=data,
          x tick label style={rotate=45,anchor=east},
        ]
        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,2) 
          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,0)};
        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,0) 
          (Snow-R1,0) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,0)};
        \addplot+[ybar] plot coordinates {(Octa-R1,6) (Octa-R2,6)
          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
        \addplot+[ybar] plot coordinates {(Octa-R1,4) (Octa-R2,2) 
          (Snow-R1,0) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
       % \legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
    \end{tikzpicture}
  \end{center}
  \caption{Adaptive timings H vs. rafined (tout : adaptatif, 2 rayons par formes, 4
    formes + images).}
  \label{fig:timings}
\end{figure}
